Anonymous provision of services via blockchain

### 2022-03-08 access.tex
small fixes to paper

Customer has delivered the package:

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its
    materials but has not paid anything, so we assume he is in neutral
    position. One would argue that the customer has put effort into
    delivering the materials to the SP or that the sample is valuable.
    We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he did not put any effort also the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:

>>>>

The customer has delivered the package:

@@

  \item
    \(\sigma_{1, c, \mathrm{n}} = \sbullet\), the customer has risked its materials but has not paid anything, so we assume he is in a neutral position. One would argue that the customer has put effort into delivering the materials to the SP or that the sample is valuable. We assume that the sample without personal information is useless, and the effort to deliver the package is negligible.
  \item
    \(\sigma_{1, s, \mathrm{n}} = \sbullet\), the SP is in the neutral position as he did not put any effort also the package has not brought any value to the SP.
  \end{itemize}
\item
  Starting a dispute:
